---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usaidplot

<!-- badges: start -->
<!-- badges: end -->

The goal of usaidplot is to apply USAID's color palette to ggplot2 graphs. This package is based on the [USAID graphic standards manual](https://www.usaid.gov/sites/default/files/2022-05/USAID_GSM-02_04_2020.pdf) and inspired by the BBC's plotting package, [bbplot](https://github.com/bbc/bbplot). Special thanks to  [sheitin](https://github.com/sheitin) for helping get this thing off of my computer and into the world.

## Installation

You can install the development version of usaidplot like so:

``` r
# install.packages("devtools")
devtools::install_github("jacobpstein/usaid_plot")
```

## Example Usage

One neat thing about this package is that you can apply the USAID color palette to either discrete or continuous data without much effort. 

Let's look at a continuous example first using R's mtcars data. We specify `data_type="continous"` to apply USAID's color palette to continuous data. 
```{r example}
library(usaidplot)
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point(aes(fill = gear), shape = 21, stroke = 1, col = "white", size = 6) + 
  usaid_plot(data_type = "continuous")

```

Now, let's make the same plot, but apply discrete colors using `data_type="discrete"`, which is also the default. 

```{r}

# we'll make gear a factor to change it from continous to discrete
ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point(aes(fill = factor(gear)), shape = 21, stroke = 1, col = "white", size = 6) + 
  usaid_plot(data_type = "discrete") # you can also just leave this blank

```

## Changing the background for presentations

USAID's PowerPoint presentation [template](https://www.usaid.gov/branding/resources) has a grey background. In some cases, users may want to avoid the white-grey contrast when they import figures into this template. Using the `ppt=TRUE` option changes the background for all figures to match the USAID slide template. The default is `ppt=FALSE`.

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point(aes(fill = gear), shape = 21, stroke = 1, col = "white", size = 6) + 
  usaid_plot(data_type = "continuous", ppt = TRUE)

```

